Verifying Demonstrations

### 2020-03-13 paper/ZKPK-instantiations.tex

\begin{figure*}
  %\centering
  \small
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \midrule

@@

  \end{tabular}
  \caption{%
    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}]\) using 
    the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}

@@

  \begin{algorithmic}
    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
        \State{\Return{$\top$}}
      \EndIf{}
      \State{\Return{$\bot$}}
    \EndFunction{}
  \end{algorithmic}
  \caption{%
    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
  }%
  \label{SPKalgorithms}
\end{figure}

>>>>

\begin{figure*}
  %\centering
  \small
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \midrule

@@

  \end{tabular}
  \caption{%
    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}]\) using 
    the Schnorr identification scheme~\cite{Camenisch-phdthesis}.
  }%
  \label{PKalgorithms}
\end{figure*}

@@

  \begin{algorithmic}
    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
        \State{\Return{$\top$}}
      \EndIf{}
      \State{\Return{$\bot$}}
    \EndFunction{}
  \end{algorithmic}
  \caption{%
    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
    using the Fiat-Shamir heuristic on the Schnorr identification 
    scheme~\cite{Camenisch-phdthesis}.
  }%
  \label{SPKalgorithms}
\end{figure}
